Title

### 2021-05-14 StateOfPractice/Peter-Notes/Report/Report.tex
added draft organization of report and purpose of report, and a few other small changes

\subsection{Purpose of Report}
-constitutes the author’s M. Eng. Report
-It is therefore intended for the examination committee

@@

@@

\subsection{Scope of Report}
-measured 23 software projects
- other limitations
- addresses what was done
- notes how things can be improved

\subsection{Organization of Report}
-organization of the document

@@

@@

\newpage
\section{Method - DONE SECTION 1st DRAFT}

@@

\newpage
\section{Answers To Research Questions}\label{answersquestions}

@@

- key findings restated
- comment on future work

@@

\subsection{Interview Questions}\label{interviewquestions}

>>>>

\subsection{Purpose of Report}

This document constitutes the author's M.Eng. report in partial fulfillment of the the degree of Master of Engineering. It is to be submitted to the Department of Computing and Software in McMaster University's Faculty of Engineer and is intended for review by the examination committee. In this context the purposes of the report are the following:

\begin{itemize}
	\item Describe the State of Practice of SCS project origin, motivations, and goals
	\item Describe LBM software structure and goals
	\item Report on the measure of a subset of LBM software packages along quality metrics
	\item Evaluate the state of practice of LBM software development along quality metrics
	\item Suggest future work for improving LBM software along quality metrics
	\item Suggest future work for improving State of Practice of SCS assessments
\end{itemize}

@@

simple about SCS ....

@@

\subsection{Scope of Report}
-measured 23 software projects (remove this)
- other limitations about the study
- addresses what was done
- notes how things can be improved

\subsection{Organization of Report}

The first part of this document includes the Table of Contents, List of Figures, and List of Tables. This is followed by Reference Material including a subsections outlining Software Engineering Related Definitions and Acronyms and Lattice Boltzmann Related Definitions and Acronyms.

The rest of core of the report is organized as follows:

\begin{itemize}
	\item \textbf{Introduction} to the report, including its purpose, motivation, scope, and organization.
	\item \textbf{Background} of Scientific Computing Software, including software qualities and software families.
	\item LBM software \textbf{Domain Analysis}.
	\item \textbf{Methodology} of this State of the Practice Assessment, including the steps of the methodology, definitions of software qualities and how they are applied in this assessment, and an overview of candidate software selection, empirical measures, and the analytical hierarchy process. 
	\item Quantitative and qualitative \textbf{Results}. 
	\item An analysis of the results and \textbf{Answers To Research Questions}.
	\item \textbf{Conclusion} to the report including comments on future State of Practice assessments.
	\item \textbf{Appendix}: This section includes our Research Questions, the Measurement Template, Grading Template, Ethics Approval, and Developer Interview Questions.
\end{itemize}

@@

this is about scs background

@@

\newpage
\section{Methodology - DONE SECTION 1st DRAFT}

@@

\section{Answers To Research Questions}\label{answersquestions}

@@

- key findings restated
- comment on future work in State of Practice SCS

@@

\subsection{Developer Interview Questions}\label{interviewquestions}
